FinalManuscript_DISCS_UG

### 2019-03-06 parts/02_relatedliterature_06fullyhomomorphic.tex
Add chapter 4 contents

We will also be testing fully homomorphic cryptosytems (FHEs), which allow aribitrary computation on encrypted data.

The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices. Gentry's original construction showed that fully homomorphic cryptosystems are possible, although they are known to be significantly slower than partially homomorphic cryptosytems. 
Improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.

We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research. Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe pertinent developements and implementations of each cryptosystem.

\subsection{DGHV Cryptosystem}
In 2009, Dijk, Gentry, Halevi, and Vaikuntanathan created a fully homomorphic cryptosystem which operates primarily through elementary modular arithmetic, commonly called the DGHV cryptosystem \cite{cryptoeprint:2009:616}. This was further improved in 2011 \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys, reducing the size of secure public keys from 12.5 GB to 2.5 MB.

The DGHV cryptosystem encrypts single bits as integer ciphertexts. XOR and AND binary operations on encrypted bits are achieved by modular addition and modular multiplication on the integer ciphertexts. When operations are performed on ciphertexts, noise accumulates in the ciphertexts, which may prevent successful decryption.

A C++ implementation of the improved DGHV cryptosystem \cite{cryptoeprint:2011:440} using the GNU Multiple Precision Arithmetic Library may be found at https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants.

For small security parameters, initial experiments using the DGHV cryptosystem have shown it takes 4.38 seconds for key generation, and

@@

For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency. Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.

>>>>

We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.

We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.

\subsection{The Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.

Given a message $m \in \mathbb{Z}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_k a_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
We now decribe the correct cryptosystem.
\subsubsection{Corrected Dasgupta--Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.

The scheme defines the encryption algorithm for a message $m$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$. This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it. Through this process, each bit of the message is encrypted separately.

Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
\begin{align*}
	m_p(x) = c(x) \bmod S_k \bmod 2.
\end{align*}
Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.

Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
To eliminate noise from a polynomial ciphertext, the following refresh function is used:
\begin{align*}
	R(c(x)) = c(x) \bmod R_k.
\end{align*}

\subsubsection{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

Arbitrary computation on data can thus be achived using these bitwise operations. While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data. Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.

@@

The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper. For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency. Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.

### 2019-03-06 parts/04_results.tex
Add chapter 4 contents

\chapter{RESULTS AND DISCUSSION}
After implementing your methodology and gathering all pertinent data, in this section, you will now present the gathered data to your reader. By the end of this section, your reader should have an idea of what exactlty happened during the experiment. 
A good way to organize your results is to group them is to present them in the same order which your methodology was presented. For instance, if your methodology included the analysis of user logs, the implementation of an application, and the testing of this application, your results should flow in the same way. In addition, more often than not, you will be presenting a large volume of data, so utilize figures and tables whenever appropriate. Table 5.1 below presents one way of how to go about presenting your data. Note the table caption and headers, as mentioned in our framework.

\begin{table}[t]
\centering
\caption {Preliminary Test Result, organized by Problem Type}
\label{tab:acc_lit} 
\begin{tabular}{ c  c  c  c  c  c  c  c  c  c  c }
\hline
Problem	&Average 	&Standard 	&Average 		&Standard		&Dominant\\
Type  &Steps   &Deviation   &Duration   &Deviation   &Affective\\
  &   &(Steps)   &(s)   &(Duration)   &State\\ \hline

A1  &14   &2.30   &23.04   &3.50   &CONF\\
A2  &2   &5.36   &32.10   &2.01   &FLOW\\
A3  &31   &1.01   &28.55   &4.03   &FLOW\\
B1  &24   &4.40   &45.30   &3.30   &BOR\\
B2  &33   &2.12   &20.56   &2.21   &FLOW\\
B3  &36   &1.05   &LOSE   &1.15   &CONF\\
C1  &22   &1.33   &LOSE   &1.40   &FLOW\\
C2  &23   &3.03   &LOSE   &1.30   &FLOW\\
D1  &30   &1.79   &LOSE   &1.45   &FLOW\\
D2  &15   &1.30   &LOSE   &1.05   &FLOW\\ \hline
\end{tabular}
\end{table}

There are, however, some additional notes that must be clarified. First, given that you will be gathering a huge volume of data, you must be able to classify which of these were critical in determining the outcome of your study, and which ones need not be presented. The critical data must be presented in this section, while the minor ones may be placed in the Appendices of your paper, which will be described later in this template.

Another clarification to be noted is that the presentation of results in this section must be objective, or `as-is'. This means that you must describe your results in a way understandable to your reader without putting any form of interpretation. In effect, this section’s intent is to provide answers to ``what happened'' questions, not ``what does it mean'' questions. The interpretation of results is the subject of a later section.

Finally, because this is a presentation of what happened in the past, all tenses used in this section must be in the past form, be it active or passive. This will also be true for the preceeding sections after the study’s implementation, especially when stating the methodology.

>>>>

\chapter{RESULTS AND DISCUSSION}
The results shown in this section are gathered from the tests for intensity transformations under Paillier and DGK cryptosystems. During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e. the results vary drastically every time the same tests were done). This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.

% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.

\section{Intensity Transformations}

% \begin{table*}
% 	\centering
% 	\caption{Comparison of intensity transformations under Paillier}
% 	\label{tbl:it-pal}
% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
% 		\hline
% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
% 		\hline
% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
% 		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
% 		\hline
% 	\end{tabular}
% \end{table*}
%
% \begin{table*}
% 	\centering
% 	\caption{Comparison of intensity transformations under DGK}
% 	\label{tbl:it-dgk}
% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
% 		\hline
% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
% 		\hline
% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
% 		(#2) & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
% 		\hline
% 	\end{tabular}
% \end{table*}

Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dgk} shows the resulting images from the same tests under the DGK cryptosystem. Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.

The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set. Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dgk} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dgk} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dgk} from applying power-law transformation.

\subsection{Image Negation}
Both the Paillier and DGK cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image. In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one. While the time taken to apply image negation is comparable to that of DGK, the Paillier cryptosystem performed better in terms of encryption and decryption time.

\begin{table}[t]
	\centering
	\caption{Image negation under Paillier}
	\label{tbl:neg-pal}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
		\hline
    \end{tabular}
\end{table}

\begin{table}[t]
	\centering
	\caption{Image negation under DGK}
	\label{tbl:neg-dgk}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
		(a) & 0.000 & $\infty$ & 1.00000 & 0.509 & 0.011 & 0.450 \\
		(b) & 0.000 & $\infty$ & 1.00000 & 0.512 & 0.009 & 0.462 \\
		(c) & 0.000 & $\infty$ & 1.00000 & 0.732 & 0.018 & 0.519 \\
		(d) & 0.000 & $\infty$ & 1.00000 & 0.593 & 0.017 & 0.677 \\
		(e) & 0.000 & $\infty$ & 1.00000 & 0.607 & 0.010 & 0.454 \\
		(f) & 0.000 & $\infty$ & 1.00000 & 0.550 & 0.010 & 0.507 \\
		(g) & 0.000 & $\infty$ & 1.00000 & 0.532 & 0.010 & 0.471 \\
		(h) & 0.000 & $\infty$ & 1.00000 & 0.538 & 0.010 & 0.513 \\
		(i) & 0.000 & $\infty$ & 1.00000 & 0.606 & 0.010 & 0.519 \\
		(j) & 0.000 & $\infty$ & 1.00000 & 0.608 & 0.012 & 0.496 \\
		\hline
        \end{tabular}
\end{table}

\subsection{Logarithm Transformation}
Unlike image negation, logarithm transformation involves more operations, so the increase in processing times for both cryptosystems are expected. Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 25 seconds each under DGK. Applying the logarithm transformation under Paillier results in faster and more accurate output images (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) than under DGK (with $\text{MSE} \le 300$ and $0.61 \le \text{SSIM} \le 0.87$).

\begin{table}[t]
	\centering
	\caption{Logarithm transformation under Paillier}
	\label{tbl:log-pal}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
		\hline
        \end{tabular}
\end{table}

\begin{table}[t]
	\caption{Logarithm transformation under DGK}
	\label{tbl:log-dgk}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
		(a) & 222.196 & 24.663 & 0.83568 & 0.635 & 25.556 & 0.488 \\
		(b) & 180.941 & 25.555 & 0.75159 & 0.542 & 27.102 & 0.460 \\
		(c) & 295.227 & 23.429 & 0.61360 & 0.534 & 25.720 & 0.486 \\
		(d) & 286.799 & 23.555 & 0.76514 & 0.622 & 25.118 & 0.467 \\
		(e) & 215.389 & 24.799 & 0.66924 & 0.557 & 25.500 & 0.452 \\
		(f) & 65.621 & 29.960 & 0.83973 & 0.561 & 25.014 & 0.458 \\
		(g) & 133.007 & 26.892 & 0.74749 & 0.572 & 25.605 & 0.497 \\
		(h) & 225.269 & 24.604 & 0.70342 & 0.548 & 25.088 & 0.468 \\
		(i) & 171.073 & 25.799 & 0.83257 & 0.538 & 25.410 & 0.494 \\
		(j) & 203.214 & 25.051 & 0.86675 & 0.528 & 25.383 & 0.516 \\
		\hline
    \end{tabular}
\end{table}

\subsection{Power-Law Transformation}
Applying the power-law transformation under both cryptosystems produced less than accurate images. The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}. As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.

\begin{table}[t]
	\centering
	\caption{Power-law transformation under Paillier}
	\label{tbl:pwr-pal}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\hline
        \end{tabular}
\end{table}

When DGK was used in the power-law transformation, it failed to produce a discernible image and only resulted in an almost black image with a faint shape of a face. The mean squared errors for this case is an order of magnitude higher than the results from using Paillier. Furthermore, doing a power-law transformation under DGK is not only impractical in terms of accuracy, but also it is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.

\begin{table}[t]
	\centering
	\caption{Power-law transformation under DGK}
	\label{tbl:pwr-dgk}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
		(a) & 14777.466 & 6.435 & 0.12778 & 0.677 & 204.491 & 0.978 \\
		(b) & 13343.854 & 6.878 & 0.07894 & 0.913 & 232.692 & 0.663 \\
		(c) & 10885.568 & 7.762 & 0.09146 & 0.696 & 198.959 & 0.590 \\
		(d) & 7218.081 & 9.547 & 0.10182 & 0.658 & 160.924 & 0.461 \\
		(e) & 9994.237 & 8.133 & 0.09100 & 0.518 & 166.274 & 0.507 \\
		(f) & 19141.793 & 5.311 & 0.08388 & 0.531 & 193.571 & 0.606 \\
		(g) & 13213.915 & 6.920 & 0.09794 & 0.656 & 163.594 & 0.455 \\
		(h) & 7444.691 & 9.412 & 0.09291 & 0.522 & 160.426 & 0.463 \\
		(i) & 21349.488 & 4.837 & 0.17239 & 0.526 & 160.191 & 0.446 \\
		(j) & 13776.770 & 6.739 & 0.10769 & 0.489 & 156.763 & 0.460 \\
		\hline
    \end{tabular}
\end{table}
